### 2018-11-14 README.Rmd
update readme
update readmes

(Note that this preprint is currently outdated, but cannot be updated because the paper is under revision)

@@

```{r, echo = FALSE, message=FALSE}
set.seed(1)

@@

## Benchmarking your own method

Explanation coming soon. Feel free to make an issue or send us an e-mail if you want your method to be included.

>>>>

(Note that this preprint is currently very outdated, see below for more recent results)

@@

```{r, echo = FALSE, message=FALSE}
set.seed(3)

@@

## Installation

dynbenchmark has been tested using R version 3.5.1 on Linux. While running the methods also works on on Windows and Mac (see [dyno](https://github.com/dynverse/dyno)), running the benchmark is currently not supported on these operating system, given that a lot of commands are linux specific.

In R, you can install the dependencies of dynbenchmark from github using:

``` r
# install.packages("devtools")
devtools::install_github("dynverse/dynbenchmark")
```

This will install several other "dynverse" packages. Depending on the number of R packages already installed, this installation should take approximately 5 to 30 minutes.

On Linux, you will need to install udunits and ImageMagick:

* Debian / Ubuntu / Linux Mint: `sudo apt-get install libudunits2-dev imagemagick`
* Fedora / CentOS / RHEL: `sudo dnf install udunits2-devel ImageMagick-c++-devel`

[Docker](https://docs.docker.com/install) has to be installed to run TI methods. See https://docs.docker.com/install for instructions. For windows 10 you can install [Docker CE](https://store.docker.com/editions/community/docker-ce-desktop-windows), older windows installations require the [Docker toolbox](https://docs.docker.com/toolbox/overview/).

You can test whether docker is correctly installed by running:

```{r, message = TRUE, echo = TRUE}
dynwrap::test_docker_installation(detailed = TRUE)
```

This command will give helpful tips if some parts of the installation are missing.
